\input{template.tex}

\begin{document}

\makeheader

This year's finals of the Headis and Prime Institute's (HPI) tournaments were everything Potsdam's sports enthusiasts could have asked for.
It was a suspense-packed match between team 3 and team 7.
Not to mention the exuberant after-show-party.
When the prime-minister stood a round there was no holding back any longer.
The screw caps flew and the Mate tea flowed.
A very eager Headis tutor, however, had overdone it, he lost his balance and stumbled into the refree's table, knocking over several half-empty mate-bottles.
Ruined was the match-report.
Following the HPI's party protocol, nobody was able to remember the final result the next day.

As a student assistant, it is your task to prepare the award ceremony and you have to find out who had won the match.
All you are left with, is the liveticker, revealing which team scored which point and of course the modus of the match,
which was exclusively introduced by the prime-minister.
In order to win a match, you have to win a $N_{sets}$ sets and in order to win a set, you have be the first to score $N_{points}$.
There is no need to be 2 points in advance.
Indeed, the prime-minister cannot but let the number of sets and points needed be both prime-numbers.
As the Headis and Prime Institute is leader in the field of prime-factorization, the modus is released by a number $N$,
with $N$ being a product of two prime numbers $p_{sets}$ and $p_{points}$. Those numbers again define $N_{sets} =
p_{sets} \mod 10^{23}$ and $N_{points} = p_{points} \mod 10^{23} \geq N_{sets}$

\paragraph*{Input}

The first line of input is the product of $p_{sets}$ ($2\leq p_{sets} \leq 2^{32}$) and $p_{points}$ ($2 \leq p_{points}
\leq 2^{32}$).
Then, the second line contains a bitstring $a$, where $a_i$ is the winning team of the $i^{th}$ point.

\paragraph*{Output}

Print the team which won the match.


\begin{samples}
  \sample{sample1}
  \sample{sample2}
\end{samples}

\end{document}
