\input{template.tex}

\begin{document}

\makeheader

After the four years you spend in the students dormitory you have to move to an own flat. Since you do not want to
assemble all the furniture that you want to have in your new flat on your own you ask the company \textit{Fast Furniture}
to assemble them for you.

\textit{Fast Furniture} has a lot of customers. Nevertheless, they want to tell you at what time they are going to be at
your new flat in order for you to open the door for them.  Also they want to be able to tell you how long it takes them
to assemble your furniture.

Unfortunately \textit{Fast Furniture}, even though they have endlessly many employees and can parallelize
as much as possible, only knows the time it takes to complete one assembly step and in which
order these steps need to be executed but they do not know the overall time it takes them to assemble.
All tasks that are before one task need to be finished before a new one can be started.


\paragraph*{Input}

The first line contains $n$ $(1\leq n \leq 10^5)$ the number of steps that need to be done to assemble that piece of furniture.

Then $n$ numbers $t$ $(1\leq t \leq 100)$ follow which represent the time it takes to finish each step.

The next line contains $m$ $(1 \leq m \leq 2 * 10^5)$ the number of instructions of which step need to be completed before the next one starts. Followed
by $m$ lines containing instructions $a$ and $b$ $(1 \leq a, b \leq n)$ saying step $a$ needs to be finished before $b$ can start.

\paragraph*{Output}

Duration that it takes to build the referred piece of furniture.

\begin{samples}
  \sample{sample1}
  \sample{sample2}
\end{samples}

\end{document}