\input{template.tex}

\begin{document}

\makeheader

Once upon a time there was a cute princess called Farida living in a castle with her father, mother and uncle.
You almost married her, just when your plan had gone terribly wrong...

On the way to the castle there lived many monsters.
Each one of them had some gold coins.
These monsters won't hurt anything except your heart.
But they would only give you their gold coin, if you didn't take coins from a monster they directly knew about.
Since these monsters only have half an eye, you expected them to only be aware of their two direct neighbours.
What a fool you had been.
Of course there would be some gossip going around.
Then, only a few monsters before reaching the castle, you've been caught!

Since farida is still a cute princess just waiting to be rescued by a clever computer scientist, you had the interactions of those monsters observed for weeks.
Now that you know their social connections, you are ready for the next attempt.

\paragraph*{Input}

The first line contains the numbers $n$ and $m$, describing the number of monsters and inter-monster-relationships respectively ($0 \leq n \leq 10^5$, $\max(0, n - 1) \leq m \leq \min(\binom{n}{2}, n + 8)$).
The next line contains $n$ numbers $c_i$, the number of coins each monster has ($0 \leq c_i \leq 10^9$).
Then follow $m$ lines with pairs of numbers $(u, v)$, describing a relationship between two monsters ($1 \leq u, v \leq n$).
Relationships are always symmetric. Also, all monsters know each other somehow transitively.

\paragraph*{Output}

Print the maximum number of coins you can collect.

\begin{samples}
  \sample{sample1}
  \sample{sample2}
  \sample{sample3}
\end{samples}

\end{document}